The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-22 paper/main.tex
fix typo
KM comment on Sec 3

Given this laundry-list of assumptions, a general formula for the apparent 
rate density follows:
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma_0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma_1\left({r\a\over 
    \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {q \mathrm{d}q \over 
    {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma_2\left({r\a\over 
    \mathcal{B}}, 
qM\a\right)\,
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\},
\label{eq:general_Gamma_a}
\end{align}
where 
\begin{equation}
\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
\end{equation}
and
\begin{equation}
\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
            sys}(M\a, q)} }
\end{equation}
are the dilution terms appropriate to primaries and secondaries, and as before 
${\rm BF}$ is the volume-limited binary fraction.

A derivation of Eq.~\ref{eq:general_Gamma_a} is given in the 
\hyperref[sec:appendix]{Appendix}; here we highlight its qualitative 
features.
The terms inside the curly braces $\{ \ldots \}$ are the sum of 
the apparent rate densities from singles, primaries, and secondaries.
The contribution from singles is not affected by binarity.
In the contributions from primaries and secondaries,
planets with $(r\a, M\a)$ are associated with 
systems of many different planetary and stellar properties.
This means that $n_{\rm det}(r\a, M\a)$ is given by a convolution of the 
true rate density, $\Gamma(r, M)$, and the number per unit $(r\a, M\a)$ of 
searchable stars that give $(r\a, M\a)$  when the true system actually has 
$(r, M)$.
This convolution has been evaluated, leaving only a dependence on the mass 
ratio distribution.
Finally, the latter term in the apparent rate density of secondaries comes 
from a correction for the overestimated transit probability.

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate (over $0.5r_\oplus$ 
        bins) as a function of planet radius for the distribution specified by 
        Eq.~\ref{eq:model3_radius_distribution}. 
        This model assumes that the true properties of all the singles and 
        primaries are known to the observer, and that the volume-limited mass 
        ratios of secondaries are drawn from a uniform distribution. We use an 
        arbitrary normalization of $Z_0=0.5$ throughout.
        The rate (left) and rate density (right) are related by $\Lambda|_a^b 
        = \int_{a}^{b}\Gamma\,{\rm d}r$.
    }
    \label{fig:occ_rate_model_3_log}
\end{figure}

>>>>

Given this laundry-list of assumptions, a general formula for the apparent 
rate density follows:
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma_0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int \mathrm{d}q \,
       \frac{f(q)}{\mathcal{A}^3}\cdot
       \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
    \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\},
\label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}$ is the volume-limited binary fraction, and $\mathcal{A}$ 
($\mathcal{B}$) is the dilution term for primaries (secondaries).
The dilution terms can be written
\begin{equation}
\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
= (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
            sys}(M\a, q)} }
= q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
former are more general).

A derivation of Eq.~\ref{eq:general_Gamma_a} is given in the 
\hyperref[sec:appendix]{Appendix}; here we highlight its qualitative 
features.
The terms inside the curly braces $\{ \ldots \}$ are the sum of 
the apparent rate densities from singles, primaries, and secondaries.
The contribution from singles is not affected by binarity.
In the contributions from primaries and secondaries,
planets with $(r\a, M\a)$ are associated with 
systems of different planetary and stellar properties, as determined
by the mass ratio $q$ of each binary.
This corresponds to true planet radii and stellar masses 
$(r\a/\mathcal{A},M\a)$ for primaries, and $(r\a/\mathcal{B},qM\a)$ for 
secondaries.
These contributions are then integrated over the mass ratio distribution 
including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$, discussed 
further below. Finally, the latter term in the apparent rate density of 
secondaries comes from a correction for the overestimated transit probability.

@@

\begin{figure}[!t]
    \centering
    \epsscale{1.15}
    \plottwo{figures/int_rate_density_vs_radius_model_3_rpu_22.5_manyZs.pdf}{figures/int_occ_rate_vs_radius_model_3_rpu_22.5_manyZs.pdf}
    \caption{
        {\it Left:} rate density and {\it right:} rate (over $0.5r_\oplus$ 
        bins) as a function of planet radius for the distribution specified by 
        Eq.~\ref{eq:model3_radius_distribution}. 
        This model assumes that the true properties of all the singles and 
        primaries are known to the observer, and that the volume-limited mass 
        ratios of secondaries are drawn from a uniform distribution. We use an 
        arbitrary normalization of $Z_0=0.5$ throughout.
        The rate and rate density are related by $\Lambda|_a^b 
        = \int_{a}^{b}\Gamma\,{\rm d}r$.
    }
    \label{fig:occ_rate_model_3_log}
\end{figure}
